---
title: "pool_analysis"
author: "Rose-Marie Fraboulet"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# **Stage M1 - Analyse de l’hétérogénéité tumorale du cancer du pancréas par des approches single-cell**

## **Loading packages**
```{r , include=FALSE}
library(Seurat)
library(ggraph)
library(ggplot2)
```


## **Loading dataset**
```{r , include=FALSE}
#Creation of a new seurat object : subset of cells from specific clusters
#Idents(pool) <- "seurat_clusters"
#pool_subset <- subset(x=pool, idents=c("2", "9", "14", "18", "20", "24", "25"))
#pool_subset
#11467 cells 

load("/home/rose/Documents/projet_stage/data/data/pool_subset.RData")
```

## **Standard pre-processing workflow - Data filtering**
## Calculate the percentage of mitochondrial genes 
```{r, echo=FALSE}
pool_subset[["percent.mt"]] <- PercentageFeatureSet(object = pool_subset, pattern = "^MT-")
head(pool_subset@meta.data, 5)
```

## **Normalizing data - logNormalize**
## Normalizing the data
```{r, echo=FALSE}
pool_subset <- NormalizeData(pool_subset)
```

### Identification of highly variable features
```{r, echo=FALSE}
pool_subset <- FindVariableFeatures(object=pool_subset, selection.method = "vst", nfeatures = 2000)
```

## **Scaling data**
```{r, include=FALSE}
pool_subset <- ScaleData(pool_subset)
```

## **Perform linear dimensional reduction**
### Dataset
```{r, include=FALSE}
pool_subset <- RunPCA(pool_subset, features = VariableFeatures(object = pool_subset))
DimHeatmap(pool_subset, dims=10:20, cells=500, balanced=TRUE)
```

## **Determine the ‘dimensionality’ of the dataset**
```{r, include=FALSE}
ElbowPlot(pool_subset, ndims = 50, reduction = "pca")
```

## **Cluster the cell**
### Shared Nearest Neighbor (SNN) Graph
```{r, echo=FALSE}
pool_subset <- FindNeighbors(pool_subset, reduction='pca', dims = 1:17)
pool_subset <- FindClusters(pool_subset, resolution = 0.5)
```

## **Run non-linear dimensional reduction**
### Uniform Manifold Approximation and Projection (UMAP) 
```{r, echo=FALSE}
pool_subset <- RunUMAP(pool_subset, dims = 1:17)
plot2 <- DimPlot(pool_subset, reduction="umap", pt.size=0.6, label=T)
plot3 <- DimPlot(pool_subset, reduction="umap", pt.size=0.6, group.by="orig.ident", cols=c("skyblue1", "red2"))
```

## **Addmodulescore**
```{r}
load("~/Documents/projet_stage/data/signatures/geneSignatures.RData")

pool_subset <- AddModuleScore(pool_subset, tumorSig, name="module_score_tumor_Sig")

#plot4 <- FeaturePlot(object=pool_subset, features="module_score_tumor_Sig1", label=TRUE, repel=TRUE)
#plot4
#plot3 <- VlnPlot(pool_subset, features="module_score_tumor_Sig1", pt.size = FALSE)
#plot3 <- plot3+labs(title="CSYNotta.ClassicA")
#plot3

#Average of add_module_score
metadata_subset <- pool_subset@meta.data
metadata_subset 
matrix_subset <- aggregate(list(metadata_subset$module_score_tumor_Sig1, metadata_subset$module_score_tumor_Sig2, metadata_subset$module_score_tumor_Sig3, metadata_subset$module_score_tumor_Sig4, metadata_subset$module_score_tumor_Sig5, metadata_subset$module_score_tumor_Sig6, metadata_subset$module_score_tumor_Sig7, metadata_subset$module_score_tumor_Sig8, metadata_subset$module_score_tumor_Sig9, metadata_subset$module_score_tumor_Sig10), by=list(metadata_subset$seurat_clusters), FUN=median)
```














